OpenMPIR

### 2017-09-06 paper.tex
Begin work on Tapir section

\begin{abstract}
Optimizing compilers for task-level parallelism are still in their infancy.
This work implements a frontend which compiles a subset of OpenMP tasks to
Tapir IR. This enables analyses and optimizations previously inaccessible to
OpenMP codes. Initial performance results for the Barcelona OpenMP tasking
suite and show performance improvements over existing OpenMP compiler
implementations. 
\end{abstract}

@@

\section{Tapir} \label{Sec:Tapir}

>>>>

\author{William S. Moses}
\affiliation{\institution{MIT CSAIL}}
\email{wmoses@mit.edu}

\begin{abstract}
Optimizing compilers for task-level parallelism are still in their infancy.
This work implements a frontend which compiles a subset of OpenMP tasks to
Tapir. This enables analyses and optimizations previously inaccessible to
OpenMP codes. Initial performance results for the Barcelona OpenMP tasking
suite and show performance improvements over existing OpenMP compiler
implementations. 
\end{abstract}

@@

\section{Tapir} \label{Sec:Tapir}
Tapir is an extension to LLVM proposed by Schardl, Moses, and Leiserson
aiming to resolve issues regarding optimizing parallel code. Prior to
the introduction of Tapir, compilers would represent parallel programs
by directly translating their syntax to opaque runtime calls. This allowed
for compilers to support parallel programs, but meant that traditional 
optimizations such as code motion \cite{} or common-subexpression elimination \cite{}
weren't able to reason about parallel programs. This often led to parallel
programs running significantly slower than expected. In the Tapir project,
the authors show that it is possible to represent and optimize fork-join
parallel programs with relatively minimal modifications to the compiler: namely
the introduction of three instructions designed to interface well with an
existing compiler.

Specifically, Tapir introduces the \texttt{detach}, \texttt{reattach}, and
\texttt{sync} instructions. \wmnote{How in detail should I go here? I can talk
about these instructions on a broad level as a target for parallel tasks, or
more concretely define what they do. However, we don't seem discuss CFG's
before this so I'm not sure what level of introduction you're thinking of.}
